### 2014-03-03 Simluations/Aspatial_fast/Figures/MPA_diffs.Rmd

# combine all data into one dataframe
sim$management = rep("No MPAs",nrow(sim))
consmpa$management = rep("Few Large MPAs", nrow(consmpa))
fishmpa$management = rep("Many Small MPAs", nrow(fishmpa))
threshz$management = rep("Thresholds", nrow(threshz))
allData <- rbind(sim,consmpa,fishmpa)
```
Map equilibrium harvest as function of speed of climate velocity and harvest rate.

```{r Compare_Management,echo = FALSE, fig.width=10, fig.height=10}
sb <- trellis.par.get("strip.background") 
sb[["col"]][1] <- "lightgray"
trellis.par.set("strip.background", sb)

@@

pdf(file="foo.pdf",width=3,height=6)
contourplot(Equil.pop ~ speed * harvest | factor(management), data = allData, region=TRUE, layout = c(1,3), drape=TRUE,col.regions=rev(colorRampPalette(brewer.pal(9,"Greys"))(100)),colorkey=FALSE,labels=list(cex=.75,col="white"))
dev.off()

contourplot(Equil.pop ~ speed * -thresh | factor(management), data = threshz, region=TRUE, drape=TRUE,col.regions=rev(colorRampPalette(brewer.pal(9,"Greys"))(100)),colorkey=FALSE,labels=list(cex=.75,col="white"),scales=list( y=list(at=seq(-8,0,2),labels=round(rev(unique(threshz$thresh)/max(threshz$thresh)),3))),ylab=list(label="proportion of unharvested population below threshold"))

# replicating our figure plots

# build dataframe

>>>>

# combine all data into one dataframe
sim$management = rep("No MPAs",nrow(sim))
consmpa$management = rep("Few Large MPAs", nrow(consmpa))
fishmpa$management = rep("Many Small MPAs", nrow(fishmpa))
threshz$management = rep("Thresholds", nrow(threshz))
allData <- rbind(consmpa,fishmpa)
```
Map equilibrium harvest as function of speed of climate velocity and harvest rate.

```{r Compare_Management,echo = FALSE, fig.width=10, fig.height=10}

# lattice plot settings

sb <- trellis.par.get("strip.background") 
sb[["col"]][1] <- "lightgray"
trellis.par.set("strip.background", sb)

@@

# mpa plots

pdf(file="MPAs.pdf",width=3,height=5)
contourplot(Equil.pop ~ speed * harvest | factor(management), data = allData, region=TRUE, layout = c(1,2), drape=TRUE,col.regions=rev(colorRampPalette(brewer.pal(9,"Greys"))(100)),colorkey=FALSE,labels=list(cex=.75,col="white"))
dev.off()

#threshold plot

pdf(file="Threshold.pdf",width=3,height=3)
contourplot(Equil.pop ~ speed * -thresh | factor(management), data = threshz, region=TRUE, drape=TRUE,col.regions=rev(colorRampPalette(brewer.pal(9,"Greys"))(100)),colorkey=FALSE,labels=list(cex=.75,col="white"),scales=list( y=list(at=seq(-8,0,2),labels=round(rev(unique(threshz$thresh)/max(threshz$thresh)),3))),ylab=list(label="proportion below threshold"))
dev.off()
